Who does big team science?

### 2023-03-23 manuscript_scopus.Rmd
old
old things

ggplot(pub_types, aes(type, count, fill = publication_type)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() +  
  xlab("Author Type") + 
  ylab("Percent of Paper Types") + 
  theme(legend.position = "none")

@@

DF_decade <- DF$small_first_gp %>% 
  mutate(who = "First") %>% 
  bind_rows(
    DF$small_other_gp %>% 
      mutate(who = "Other")
  ) %>% 
  mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
  group_by(who, Decade) %>% 
  summarize_all(sum) %>% 
  pivot_longer(cols = `Western Europe`:Mirconesia,
               names_to = "Country", 
               values_to = "Count")

@@

DF_decade <- DF$medium_first_gp %>% 
  mutate(who = "First") %>% 
  bind_rows(
    DF$medium_other_gp %>% 
      mutate(who = "Other")
  ) %>% 
  mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
  group_by(who, Decade) %>% 
  summarize_all(sum) %>% 
  pivot_longer(cols = `Western Europe`:Melanesia, 
               #### check this later ####
               names_to = "Country", 
               values_to = "Count")

@@

DF_decade <- DF$large_first_gp %>% 
  mutate(who = "First") %>% 
  bind_rows(
    DF$large_other_gp %>% 
      mutate(who = "Other")
  ) %>% 
  mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
  group_by(who, Decade) %>% 
  summarize_all(sum) %>% 
  pivot_longer(cols = `Western Europe`:`Central Asia`, 
               #### check this later ####
               names_to = "Country", 
               values_to = "Count")

>>>>

ggplot(pub_types, aes(type, count, fill = publication_type)) + 
    geom_bar(position="fill", stat="identity", color = "black") + 
  theme_classic() +  
  xlab("Author Type") + 
  ylab("Percent of Paper Types") + 
  theme(legend.position = "right")

@@

DF_decade <- DF$small_first_gp %>% 
  mutate(who = "F") %>% 
  bind_rows(
    DF$small_other_gp %>% 
      mutate(who = "O")
  ) %>% 
  mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
  group_by(who, Decade) %>% 
  summarize_all(sum) %>% 
  pivot_longer(cols = `Western Europe`:Mirconesia,
               names_to = "Country", 
               values_to = "Count")

@@

DF_decade <- DF$medium_first_gp %>% 
  mutate(who = "F") %>% 
  bind_rows(
    DF$medium_other_gp %>% 
      mutate(who = "O")
  ) %>% 
  mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
  group_by(who, Decade) %>% 
  summarize_all(sum) %>% 
  pivot_longer(cols = `Western Europe`:Melanesia, 
               #### check this later ####
               names_to = "Country", 
               values_to = "Count")

@@

DF_decade <- DF$large_first_gp %>% 
  mutate(who = "F") %>% 
  bind_rows(
    DF$large_other_gp %>% 
      mutate(who = "O")
  ) %>% 
  mutate(Decade = ifelse(Year < 1990, "1980s", 
                         ifelse(Year < 2000, "1990s", 
                                ifelse(Year < 2010, "2000s", 
                                       ifelse(Year < 2020, "2010s", "2020s"))))) %>% 
  group_by(who, Decade) %>% 
  summarize_all(sum) %>% 
  pivot_longer(cols = `Western Europe`:`Central Asia`, 
               #### check this later ####
               names_to = "Country", 
               values_to = "Count")
